---
title: "Download functions in massdatabase"
author:
- name: Xiaotao Shen (https://www.shenxt.info/)
date: "Created on 2022-05-30 and updated on `r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: no
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{download_functions}
  %\VignettePackage{massdatabase}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = TRUE,
  out.width = "100%"
)
```

"Download functions" is series functions that could be used to download online databases.

# **BIGG model database**

[BIGG model](http://bigg.ucsd.edu/)is a knowledge base of genome-scale metabolic network reconstructions.

Download the BIGG model data

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
library(massdatabase)
```

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_bigg_model(model_id = "iND750")
```

Download the BIGG universal metabolite database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_bigg_universal_metabolite(path = ".", sleep = 1)
```


# **ChEBI database** 

Chemical Entities of Biological Interest ([ChEBI](https://www.ebi.ac.uk/chebi/)) is a freely available dictionary of molecular entities focused on ‘small’ chemical compounds.

Download ChEBI compound database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_chebi_compound(path = ".")
```

# **FooDB database** 

[FooDB](https://foodb.ca/) is the world’s largest and most comprehensive resource on food constituents, chemistry and biology.

Download the FooDB compound database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_foodb_compound(compound_id = "all", path = ".")
```


# **GNPS database** 

The [GNPS](https://gnps-external.ucsd.edu/gnpslibrary) GNPS is a web-based mass spectrometry ecosystem that aims to be an open-access knowledge base for community-wide organization and sharing of raw, processed, or annotated fragmentation mass spectrometry data (MS/MS). GNPS aids in identification and discovery throughout the entire life cycle of data; from initial data acquisition/analysis to post publication.

Download one GNPS compound database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_gnps_spectral_library(gnps_library = "HMDB", path = ".")
```

# **KEGG database** 

[KEGG](https://www.genome.jp/kegg/) is a database resource for understanding high-level functions and utilities of the biological system, such as the cell, the organism and the ecosystem, from molecular-level information, especially large-scale molecular datasets generated by genome sequencing and other high-throughput experimental technologies.

Download KEGG compound database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_kegg_compound(path = ".")
```

Download KEGG pathway database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_kegg_pathway(path = ".", organism = "hsa")
```

Download KEGG reaction class database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_kegg_rclass()
```


Download KEGG drug database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_kegg_drug(path = ".")
```

# **LipidBank**

The official database of Japanese Conference on the Biochemistry of Lipids (JCBL). [Link](https://lipidbank.jp/)


Download the LipidBank lipid class database.

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_lipidbank_lipid_class(lipid_class = "Acylglycerol", path = ".")
```

# **LipidMaps**

[LIPID MAPS Lipidomics Gateway](https://www.lipidmaps.org/) was created in 2003 via an NIH “Glue Grant” to provide access to lipid nomenclature, databases, tools, protocols, standards, tutorials, meetings, publications, and other resources and serving the international lipid research community.

Download lipidmaps database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_lipidmaps_lipid(path = ".")
```

# **MassBank**

[MassBank](https://massbank.eu/MassBank/) is a community effort and you are invited to contribute. Please refer to our contributor documentation and get in touch via github or email.

Download MassBnak compound database.

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_massbank_compound(source = "nist")
```

# **SMPDB**

[SMPDB](https://www.smpdb.ca/) is an interactive, visual database containing more than 30000 small molecule pathways found in humans only.

Download SMPDB pathway database.

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
download_smpdb_pathway(path = ".")
```



# **Session information**

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```


