---
title: "KEGG compound"
author:
- name: Xiaotao Shen (https://www.shenxt.info/)
date: "Created on 2022-05-11 and updated on `r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: no
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{kegg_compound}
  %\VignettePackage{massdatabase}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = TRUE,
  out.width = "100%"
)
```

# **Request**

Get the information of all compounds in KEGG (https://www.genome.jp/kegg/compound/).

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
library(massdatabase)
compound_info <- 
  request_kegg_compound_info()
head(compound_info)
```

During the installation, it will ask if you want to update some packages for few times, just enter `enter` key to skip it.

# **Install `metdatabase` from GitHub**

You can just use the `remotes` to install `metdatabase`. 

```{r,eval=FALSE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
remotes::install_github("tidymass/metdatabase", dependencies = TRUE)
```

During the installation, it will ask if you want to update some packages for few times, just enter `enter` key to skip it.

If there is a error like below:

```
Error: Failed to install 'metdatabase' from GitHub: HTTP error 403. API rate limit exceeded for 171.66.10.237. (But here's the good news: Authenticated requests get a higher rate limit. Check out the documentation for more details.)
```

Try to resolve it by:

1. In you R console, type this code:

```{r,eval=FALSE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
usethis::create_github_token()
```

It will open a page in browser, and create a "New personal access token" and copy it.

2. Then type this code:

```{r,eval=FALSE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
usethis::edit_r_environ()
```

and then add one line like below:

```
GITHUB_PAT=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
```
> The `GITHUB_PAT` should be yours that is created in step 1.

And then restart R session and try again.


[Let me know if you have any questions](shenxt1990@outlook.com).

# **Session information**

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```


