---
title: "Read and convert downloaded databases in massdatabase"
author:
- name: Xiaotao Shen (https://www.shenxt.info/)
date: "Created on 2022-05-30 and updated on `r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: no
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{read_convert_functions}
  %\VignettePackage{massdatabase}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = TRUE,
  out.width = "100%"
)
```

"Read functions" is series functions that could be used to read downloaded online databases. And "convert functions" is series functions that could be used to convert them to other formats.

# **BIGG model database**

[BIGG model](http://bigg.ucsd.edu/)is a knowledge base of genome-scale metabolic network reconstructions.

Read and convert the BIGG model data

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
library(metid)
library(massdatabase)
library(metpath)
```

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data <- 
  read_bigg_universal_metabolite(path = ".")
bigg_database <- 
  convert_bigg_universal2metid(data = data, path = ".")
```

# **ChEBI database** 

Chemical Entities of Biological Interest ([ChEBI](https://www.ebi.ac.uk/chebi/)) is a freely available dictionary of molecular entities focused on ‘small’ chemical compounds.

Read and convert ChEBI compound database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data <-
  read_chebi_compound(path = ".")
chebi_database <-
  convert_chebi2metid(data = data, path = ".")
```

# **FooDB database** 

[FooDB](https://foodb.ca/) is the world’s largest and most comprehensive resource on food constituents, chemistry and biology.

Read and convert the FooDB compound database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data <- 
  read_foodb_compound(path = ".")
foodb_dataabse <- 
  convert_foodb2metid(data = data, path = ".")
```


# **GNPS database** 

The [GNPS](https://gnps-external.ucsd.edu/gnpslibrary) GNPS is a web-based mass spectrometry ecosystem that aims to be an open-access knowledge base for community-wide organization and sharing of raw, processed, or annotated fragmentation mass spectrometry data (MS/MS). GNPS aids in identification and discovery throughout the entire life cycle of data; from initial data acquisition/analysis to post publication.

Read and convert one GNPS compound database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data <-
  read_msp_data_gnps(file = "ms2.msp")
gnps_database <- 
  convert_gnps2metid(data = data, path = ".")
```

# **KEGG database** 

[KEGG](https://www.genome.jp/kegg/) is a database resource for understanding high-level functions and utilities of the biological system, such as the cell, the organism and the ecosystem, from molecular-level information, especially large-scale molecular datasets generated by genome sequencing and other high-throughput experimental technologies.

Read and convert KEGG compound database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data <- 
  read_kegg_compound(path = ".")
kegg_database <-
  convert_kegg2metid(data = data, path = ".")
```

Read and convert KEGG pathway database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data <- 
  read_kegg_pathway(path = ".")
kegg_pathway_database <-
  convert_kegg2metpath(data = data, path = ".")
```


# **LipidMaps**

[LIPID MAPS Lipidomics Gateway](https://www.lipidmaps.org/) was created in 2003 via an NIH “Glue Grant” to provide access to lipid nomenclature, databases, tools, protocols, standards, tutorials, meetings, publications, and other resources and serving the international lipid research community.

Read and convert lipidmaps database

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data <-
  read_sdf_data_lipidmaps(file = "data.sdf", path = ".")
lipidmaps_database <-
  convert_lipidmaps2metid(data = data, path = ".")
```

# **MassBank**

[MassBank](https://massbank.eu/MassBank/) is a community effort and you are invited to contribute. Please refer to our contributor documentation and get in touch via github or email.

Read and convert MassBnak compound database.

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data <- read_msp_data_massbank(file = "data.msp")
massbank_database <- 
  convert_massbank2metid_nist(data = data, path = ".")
```

# **SMPDB**

[SMPDB](https://www.smpdb.ca/) is an interactive, visual database containing more than 30000 small molecule pathways found in humans only.

Read and convert SMPDB pathway database.

```{r,eval=FALSE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
data <- 
  read_smpdb_pathway(path = ".", only_primarity_pathway = TRUE)
smpdb_pathway_database <-
  convert_smpdb2metpath(data = data, path = ".")
```



# **Session information**

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```


