---
title: "Request functions in massdatabase"
author:
- name: Xiaotao Shen (https://www.shenxt.info/)
date: "Created on 2022-05-11 and updated on `r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: no
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{request_functions}
  %\VignettePackage{massdatabase}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = TRUE,
  out.width = "100%"
)
```

"Request functions" is series functions that could be used to request one specific compound/pathway information using web crawler.

# **BIGG model database**

[BIGG model](http://bigg.ucsd.edu/)is a knowledge base of genome-scale metabolic network reconstructions.

Get the BIGG model information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
library(massdatabase)
x <- 
  request_bigg_model_info()
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
dim(x)
head(x)
```

Get the BIGG universal metabolite information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
library(massdatabase)
x <- 
  request_bigg_universal_metabolite_info()
```

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
dim(x)
head(x)
```


Get one specific metabolite information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_bigg_universal_metabolite(metabolite_id = "g3p", 
                                    return_form = "list")
names(x)
x$database_link
```

Get universal reaction information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_bigg_universal_reaction_info()
dim(x)
head(x)
```

Get one specific reaction information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_bigg_universal_reaction(reaction_id = "ADA", 
                                  return_form = "list")
names(x)
x$reaction_string
```

Get BIGG model version.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
request_bigg_version()
```

# **ChEBI database** 

Chemical Entities of Biological Interest ([ChEBI](https://www.ebi.ac.uk/chebi/)) is a freely available dictionary of molecular entities focused on ‘small’ chemical compounds.

Get one specific ChEBI compound information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_chebi_compound(compound_id = "CHEBI:18358")
names(x)
x$base_info
```

# **FooDB database** 

[FooDB](https://foodb.ca/) is the world’s largest and most comprehensive resource on food constituents, chemistry and biology.

Get the FooDB compound information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_foodb_compound_info()
dim(x)
head(x)
```

Get one specific FooDB compound information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_foodb_compound(compound_id = "FDB000004", 
                         return_form = "list")
names(x)
x[1:5]
```

Get one specific FooDB compound MS2 spectrum.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_foodb_compound_ms2(compound_id = "FDB000004")
names(x)
x$`142524`
```

# **HMDB database** 

The [Human Metabolome Database (HMDB)](https://hmdb.ca/) is a freely available electronic database containing detailed information about small molecule metabolites found in the human body.

Get one specific HMDB compound information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_hmdb_metabolite(metabolite_id = "HMDB0000001",
                          return_form = "list")
names(x)
head(x)
```

# **KEGG database** 

[KEGG](https://www.genome.jp/kegg/) is a database resource for understanding high-level functions and utilities of the biological system, such as the cell, the organism and the ecosystem, from molecular-level information, especially large-scale molecular datasets generated by genome sequencing and other high-throughput experimental technologies.

Get all KEGG compound information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_kegg_compound_info()
dim(x)
head(x)
```

Get one specific KEGG compound information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_kegg_compound("C02886", "list")
names(x)
x
```

Get all KEGG drug information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_kegg_drug_info()
dim(x)
head(x)
```

Get one specific KEGG drug information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_kegg_drug("D00001", "list")
names(x)
x
```


Get all KEGG reaction class (rclass) information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_kegg_rclass_info()
dim(x)
head(x)
```

Get one specific KEGG reaction information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_kegg_reaction(reaction_id = "R00001")
names(x)
x
```

Get all pathway information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_kegg_pathway_info(organism = "hsa")
dim(x)
head(x)
```

Get one specific pathway information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_kegg_pathway(pathway_id = "hsa00010")
names(x)
x
```

# **LipidBank**

The official database of Japanese Conference on the Biochemistry of Lipids (JCBL). [Link](https://lipidbank.jp/)


Get the LipidBank lipid class.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_lipidbank_lipid_class(lipid_class = "Wax")
dim(x)
head(x)
```

# **LipidMaps**

[LIPID MAPS Lipidomics Gateway](https://www.lipidmaps.org/) was created in 2003 via an NIH “Glue Grant” to provide access to lipid nomenclature, databases, tools, protocols, standards, tutorials, meetings, publications, and other resources and serving the international lipid research community.

Get one specific lipid information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_lipidmaps_lipid(lipid_id = "LMFA01030001")
x
```

# **WikiPedia**

We can also get information from WikiPedia.

Get one specific compound information.

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_wikipedia_compound(compound_id = "Microcystin-LR")
dim(x)
head(x)
```

Get the classification of one species

```{r,eval=TRUE,warning=FALSE, R.options="", message=TRUE, cache=TRUE}
x <- 
  request_wikipedia_scientific_classification(species_id = "Aaptos ciliata")
dim(x)
x
```

# **Session information**

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```


